---
title: "Report exercise 3.5"
output: html_document
date: "2023-03-06"
---

In this exercise, a dataset about decomposition is being manually cleaned, using R and then wrangled with. 


the first part of this exercise includes downloading the data set, reading it into R, cleaning it manually and then exporting it as a csv file. 

I will start by downloading it and reading it into R:

```{r}



#install.packages("readxl")
#package that allows reading excel files into R

library(readxl)

data <- read_excel("/Users/sina/Downloads/1249534s1-s6.xlsx",
                   sheet = 1) #Important, because file has multiple sheets, called Databases here


View(data)

```

I now start cleaning it further. The first step here would be to get the names of the columns right. As i see it, the row 3 represents the right and actual column names. So I will now try to make those the header names of the columns. I then dropped the first 4 rows as they are empty.

Here I used the Janitor package, that was suggested to me by Google to delete rows that only include NAs. I then used the tidyr package to be able to expand the experiment names to all the rows that they should be in.


```{r}
#install.packages("tidyverse")
library(tidyverse)
library(tidyr)

names(data) <- data[3,]

data <- data %>% rename("n ambient CO2" = 8,
                        "n increased CO2" = 9,
                        "description of data source" = 10,
                        "Value treatment bulk density" = 11,
                        "mean ambient CO2" = 6,
                        "mean increased CO2" = 7)

#Here I took care of the names of the columns


View(data)


data <- data[-(1:4),]

#Here I dropped the first few (empty) rows

#install.packages("janitor")
library(janitor)

data <- janitor::remove_empty(data, which = "rows")

View(data)


data <- data %>% unnest(Experiment)

data <- data %>% fill(Experiment)

#I had to unnest the data before I could fill the empty spaces in the Experiment column

data <- data %>% 
  separate(col = Depth,
           into = c("0", "Depth 0 to... in cm", "cm")) 

data <- data[-c(3,5)]

# Here I got rid of the cm measure in the depth column

data$`Sample date` <- gsub("[a-zA-Z./]", "", data$`Sample date`)
data$`Value treatment bulk density` <- gsub("[a-zA-Z=,./():]", "", data$`Value treatment bulk density`)

#Here I tried to get rid of the description in the bulk density column -> was only semi sucesful

write_csv(data, file = "/Users/sina/Downloads/tidy_data_report_exercise_1.csv")

knitr::kable(data)

#Here I exported the data as a csv file


```

Now that the data is relatively tidy we can start with the second part of the exercise.

I firstly make the data numeric, then group it by experiment and summarize it by mean. It is important to remove the missing values or else it cant calculate the mean (took me long enough to remember that one ;)). I used the package SciViews because they have a ln function which is needed to calculate the log-response ratio.


```{r}

data <- read_csv("/Users/sina/Downloads/tidy_data_report_exercise_1.csv")

data$`mean ambient CO2` <- as.numeric(data$`mean ambient CO2`)

data$`mean increased CO2` <- as.numeric(data$`mean increased CO2`)

data$`Time (years)` <- as.numeric(data$`Time (years)`)

#Here I made the important variables numeric

aggregated_data_per_experiment <- data %>% 
  group_by(Experiment) %>% 
  summarise_at(c("mean ambient CO2", "mean increased CO2"), mean, na.rm = T)

#Here I aggregated the data by experiment and summarized by mean of the CO2 variables
  
View(aggregated_data_per_experiment)

#install.packages("SciViews")
library(SciViews)

aggregated_data_per_experiment <- aggregated_data_per_experiment %>% 
  mutate(RR = ln(`mean increased CO2`/`mean ambient CO2`))

#Here I calculate the log response ratio

View(aggregated_data_per_experiment)

knitr::kable(aggregated_data_per_experiment)

```

Now for the third part of the exercise, I need to aggregate across all experiments for different years.

Then I need to classify into an early phase (<3), a mid phase (3-6) and a late phase (>6) and also caluclate the log repsonse ratio.

```{r}

aggregated_data_group_by_year <- data %>% 
  mutate(time = cut(`Time (years)`,
                     breaks = c(0,3,6,200), labels = c("early phase", "mid-phase", "late phase"),
                    inlcude.lowest = T, na.rm = T)) %>% 
  group_by(time) %>% 
  summarise_at(c("mean ambient CO2", "mean increased CO2"), mean, na.rm = T)

aggregated_data_group_by_year <- aggregated_data_group_by_year[-4,]

#Here I got rid of the NA rows

aggregated_data_group_by_year <- aggregated_data_group_by_year %>% 
  mutate(RR = ln(`mean increased CO2`/`mean ambient CO2`))

#Here I calculated the log-response ratio
  
View(aggregated_data_group_by_year)

knitr::kable(aggregated_data_group_by_year)


```








